Repeatability Test

### 2018-05-18 pt_characterization/machine_cons_check/paper.tex
Rick's comments & INC data

\paragraph{Experimental Notes:} In our experiments 
we used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12} ) in the same cluster. 
A short summary of the experiments is exhibited in Table~\ref{tab:exp_notes}.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em bottom left} power strip) & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip)  &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into {\em the upper left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into {\em the upper left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

>>>>

\paragraph{Experimental Notes:} In our experiments 
we used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12}) in the same cluster. 
A short summary of the experiments is exhibited in Table~\ref{tab:exp_notes}.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em bottom left} power strip) & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip)  &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into {\em the upper left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into {\em the upper right} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

### 2018-05-18 pt_characterization/machine_cons_check/post_exp.tex
Rick's comments & INC data

\paragraph{Experimental Notes:} In the experiments 
we also used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12} ) in the same cluster. 
A short summary of the experiments is shown in Table~\ref{tab:exp_notes2}.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em bottom left} power strip) &  INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) &  IINC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes2}}
\end{table}

>>>>

\paragraph{Experimental Notes:} In the experiments 
we also used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12}) in the same cluster. 
A short summary of the experiments is shown in Table~\ref{tab:exp_notes2}.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em the upper right} power strip) &  INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) &  IINC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip) & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes2}}
\end{table}

### 2018-05-18 pt_characterization/real_data/paper.tex
Rick's comments & INC data

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
%{\tt sodb8}  (plugged into {\em bottom left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-??-?? $\sim$2018-??-??\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-04-09 $\sim$2018-04-12\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & MATC1K, MATC2K, MATC4K, MATC8K & Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & MATR1K, MATR2K, MATR4K, MATR8K& Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows. 
The program was run on {\tt sodb12} plugged into {\em the upper left} power strip.

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb8} plugged into {\em bottom left} power strip.

@@

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program. 
{\tt sodb8} was plugged into {\em bottom left} power strip 
while {\tt sodb10} plugged into {\em the upper left} power strip.

>>>>

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
%{\tt sodb8}  (plugged into {\em bottom left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-??-?? $\sim$2018-??-??\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-04-09 $\sim$2018-04-12\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & MATC1K, MATC2K, MATC4K, MATC8K & Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip) & MATR1K, MATR2K, MATR4K, MATR8K& Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows. 
The program was run on {\tt sodb12} plugged into {\em the upper right} power strip.

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb8} \underline{plugged into {\em bottom left}} power strip.

@@

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program. 
\underline{{\tt sodb8}} was plugged into \underline{{\em bottom left} power strip} 
while \underline{{\tt sodb10}} plugged into \underline{{\em the upper left} power strip}.

### 2018-05-18 pt_characterization/rep_check/res1.tex
Rick's comments & INC data

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|p{3cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip)  &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-02 $\sim$ 2017-03-04 & Figs.~\ref{fig:s9_r1_et_hist1},~\ref{fig:s9_r1_et_hist2},~\ref{fig:s9_r1_pt_hist1}, and~\ref{fig:s9_r1_pt_hist2}\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip)  &  INC128$\sim$ INC1024 & 300 samples, each & 2017-03-04 $\sim$ 2017-03-11 & 
Figs.~\ref{fig:s9_r1_et_hist3} and~\ref{fig:s9_r1_pt_hist3}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & INC2048 & 300 samples & 2017-03-02 $\sim$ 2017-03-09 & Figs.~\ref{fig:inc2048_r1_et_hist_v5} and~\ref{fig:inc2048_r1_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip)  & INC4096 & 300 samples & 2017-02-13 $\sim$ 2017-02-27 & Figs.~\ref{fig:inc4096_r1_et_hist_v5} and~\ref{fig:inc4096_r1_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes1}}
\end{table}

>>>>

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{3cm}|p{2cm}|p{3cm}|p{4cm}|p{3cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip)  &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-02 $\sim$ 2017-03-04 & Figs.~\ref{fig:s9_r1_et_hist1},~\ref{fig:s9_r1_et_hist2},~\ref{fig:s9_r1_pt_hist1}, and~\ref{fig:s9_r1_pt_hist2}\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip)  &  INC128$\sim$ INC1024 & 300 samples, each & 2017-03-04 $\sim$ 2017-03-11 & 
Figs.~\ref{fig:s9_r1_et_hist3} and~\ref{fig:s9_r1_pt_hist3}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & INC2048 & 300 samples & 2017-03-02 $\sim$ 2017-03-09 & Figs.~\ref{fig:inc2048_r1_et_hist_v5} and~\ref{fig:inc2048_r1_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip)  & INC4096 & 300 samples & 2017-02-13 $\sim$ 2017-02-27 & Figs.~\ref{fig:inc4096_r1_et_hist_v5} and~\ref{fig:inc4096_r1_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes1}}
\end{table}

### 2018-05-18 pt_characterization/rep_check/res2.tex
Rick's comments & INC data

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-13 $\sim$ 2017-03-14 & Figs.~\ref{fig:s9_r2_et_hist1},~\ref{fig:s9_r2_et_hist2},~\ref{fig:s9_r2_pt_hist1}, and~\ref{fig:s9_r2_pt_hist2}\\ \hline
%{\tt sodb9} &  INC128$\sim$INC1024 & 300 samples, each & 2017-03-14 $\sim$ 2017-03-21 & 
%Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC512$\sim$INC1024 & 300 samples, each & 2017-03-17 $\sim$ 2017-03-21 & 
Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip) & INC2048 & 300 samples & 2017-03-13 $\sim$ 2017-03-20 & Figs.~\ref{fig:inc2048_r2_et_hist_v5} and~\ref{fig:inc2048_r2_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & INC4096 & 300 samples & 2017-03-02 $\sim$ 2017-03-17 & Figs.~\ref{fig:inc4096_r2_et_hist_v5} and~\ref{fig:inc4096_r2_hist_v5}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip) & INC8192& 261 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc8192_r2_et_hist_v5} and~\ref{fig:inc8192_r2_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & INC16384& 130 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc16384_r2_et_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes2}}
\end{table}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-13 $\sim$ 2017-03-14 & Figs.~\ref{fig:s9_r2_et_hist1},~\ref{fig:s9_r2_et_hist2},~\ref{fig:s9_r2_pt_hist1}, and~\ref{fig:s9_r2_pt_hist2}\\ \hline
%{\tt sodb9} &  INC128$\sim$INC1024 & 300 samples, each & 2017-03-14 $\sim$ 2017-03-21 & 
%Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC512$\sim$INC1024 & 300 samples, each & 2017-03-17 $\sim$ 2017-03-21 & 
Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip) & INC2048 & 300 samples & 2017-03-13 $\sim$ 2017-03-20 & Figs.~\ref{fig:inc2048_r2_et_hist_v5} and~\ref{fig:inc2048_r2_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip) & INC4096 & 300 samples & 2017-03-02 $\sim$ 2017-03-17 & Figs.~\ref{fig:inc4096_r2_et_hist_v5} and~\ref{fig:inc4096_r2_hist_v5}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip) & INC8192& 261 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc8192_r2_et_hist_v5} and~\ref{fig:inc8192_r2_hist_v5}\\ \hline
{\tt sodb12} (plugged into {\em the upper right} power strip) & INC16384& 130 samples & 2017-04-27 $\sim$ 2017-05-21 & Figs.~\ref{fig:inc16384_r2_et_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes2}}
\end{table}
